Accessing biological data with semantic web technologies

### 2013-12-26 article.tex
Mapping concepts to ontologies...

Taking advantage of ...

>>>>

\begin{table}
\caption{A list of ontology terms for the concepts in the BRCA1 SNP example. Ontology acronyms and the prefixes
used are explained in the text.}
\begin{center}
\begin{tabular}{l|l|l|l}
 \textbf{concept} & \textbf{ontology} & \textbf{term} & \textbf{URI} \\
\hline
 SNP & SIO & snp & sio:SIO\_010027 \\
\end{tabular}
\end{center}
\end{table}

Taking advantage of ...
SIO is the Semanticscience Integrated Ontology;
... Prefixes used in the term Uniform Resource Identifiers (URIs) include sio for \url{http://semanticscience.org/resource/} ...
